Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Remove extra space
paper: Add conclusions, future work section.

@@

\begin{thebibliography}{9}
\bibitem{nano3}
  K. Grove-Rasmussen og Jesper Nygård,
  \emph{Kvantefænomener i Nanosystemer}.
  Niels Bohr Institute \& Nano-Science Center, Københavns Universitet

\bibitem{Bengio94}
  http://ai.dinfo.unifi.it/paolo//ps/tnn-94-gradient.pdf

\bibitem{hochreiter97}
  http://www.bioinf.jku.at/publications/older/2604.pdf

\bibitem{schwenk05}
  ftp://tlp.limsi.fr/public/emnlp05.pdf. Accessed 6 Nov. 2018.

\bibitem{Milkolov10}
  Milkolov T., et al, Recurrent neural network based language model, INTERSPEECH 2010

\bibitem{xavier10}
  Understanding the difficulty of training deep feedforward neural networks - Glorot, Xavier \& Bengio Yoshua. 2010

\bibitem{hinton2012}
  https://arxiv.org/pdf/1207.0580.pdf

\bibitem{cho2014}
  https://arxiv.org/pdf/1406.1078v3.pdf

\bibitem{colah2015}
  http://colah.github.io/posts/2015-08-Understanding-LSTMs/

\bibitem{press16}
  Using the Output Embedding to Improve Language Models - Press, Ofir \& Wolf, Lior. 2016

\end{thebibliography}

>>>>

Experimentation with model hyperparameters that increase or decrease information
retention (such as number of hidden layers or their dimensionality) peformed in line
with expectations. In general, increasing the amount of information stored by the network
allowed it to generate more marginally more realistic language with a lower degree of
perplexity at the output layers.

Usage of trainable word embeddings at the encoding layers outperformed our expectations -
we found that there were no situations where using word embeddings did not result in both
a computational performance and natural language generation performance improvement. In fact,
word embeddings resulted in the most significant perforamnce improvement out of any of the
modifications that we made to the baseline models. We also found that using output shortlists
of length 5000 or above for the WikiText models resulted in scores competitve with the baseline
on both METEOR and ROUGE, but with twice to fource times less computational complexity because
not as many dot products need to be performed at the output layer for each word prediction. However,
if one had to choose between shortlisting and trainable word embeddings at the input layer, embeddings
are able to reduce compute complexity much more whilst also improving accuracy, something that
did not happen with shortlists at the output layer.

We found that like the paper suggested, usage of regularization techniques did not assist in improving
either perplexity or scores on both METEOR and ROUGE. This was even true in the case of Dropout,
which was proposed after the 2010 paper by Milkolov was published. Such a result was surprising to us
and perhaps requires further investigation and testing. For instance, Zaremba & Vinyals found that
applying dropout on non-recurrent connections could be an effective regularizer \cite{zaremba2015},
though this is different to the way in which we implemented dropout, which was on both the recurrent
and non-recurrent connections. This may have impacted the network's ability to remember crucial
information during training that it would allow it to make better predictions and optimize better.

Finally, we found that using Tied Weights and Xavier Initialization did not assist on any of our
natural language generation metrics and in fact made performance worse. It was surprising to see
that Xavier Initialization made the model perform more poorly, so perhaps further analysis is required
as to the state of the activations between the recurrent connections to determine if they are more
or less saturated during training.

@@

In this paper, we did not have the opportunity to evaluate some of the methods identified in our
original literature review. For instance, we were not able to implement a working version of
Batch Normalization \cite{ioffe} which has been shown to be effective in the context of LSTMs \cite{courville2017}.

We also did not have the opportunity to examine Adaptive Importance Sampling \cite{bengio08}. Doing so
likely would have taken a substantial amount of time to implement as it stands in as an alternative
to full backpropagation. However, it would be useful to see if the technique is effective in
reducing the training time of the RNN models by merely approximating the converged state.

Finally, we did not get the opportunity to implement the open vocabulary approach, which would allow
the network to fall back to predicting character data if an UNK token was predicted \cite{ling2016}. Such
an approach again would have required substantial modification to the baseline implementation that
we used, since the baseline predicts one-hot encoded words in batches and is not set up to deal with
character encodings.
